Are mental properties supervenient on brain properties?

### 2011-09-16 nature_sci_rep/submission2/supervenience.tex
made decision letter response less light
waiting for proofs now

\noindent Questions and assumptions about mind-brain supervenience go back at least as far as Plato's dialogues in circa 400 BCE \cite{Plato97}.  While there are many different notions of supervenience, we find Davidson's canonical description particularly illustrative \cite{Davidson70}:
%  The mind-brain supervenience notion was canonized in 1970 with the following quote from Donald Davidson \cite{Davidson70}:
\begin{quotation}
\noindent [mind-brain] supervenience might be taken to mean that there cannot be two events alike in all physical respects but differing in some mental respect, or that an object cannot alter in some mental respect without altering in some physical respect.
\end{quotation}
Colloquially, supervenience means ``there cannot be a mind-difference without a physical-difference.''
This philosophical conjecture has potentially widespread implications.  
% We consider a special case of supervenience of considerable interest.  Specifically, this work addresses a version of a local supervenience between mental properties and brain properties, with particular emphasize on brain-graphs (i.e., connectivity structure).  Supervenience questions or assumptions are fundamental to 
% The determination of supervenience (or lack thereof) of minds on brains has potentially important implications in 
% a number of fields of inquiry.  
For example, neural network theory and artificial intelligence often implicitly assume 
% take a generalized notion of 
a local version mind-brain supervenience 
% as an assumption 
% , which if falsified, might change modern approaches to learning 
\cite{Haykin2008,Ripley2008}. Cognitive neuroscience similarly seems to operate under such assumptions
% , which if falsified, might result in novel perspectives and theories 
\cite{Gazzaniga2008}.  Philosophers continue to debate and refine notions of supervenience 
% And the question of mind-brain supervenience continues to be debated amongst philosophers 
\cite{Kim2007}.  
% Moreover, many cognitive neuroscience investigations could be cast as questions
Yet, to date, relatively scant attention has been paid to what might be empirically learned about supervenience.

@@

Let $A_{uv}$ be the number of chemical synapses between neuron $u$ and neuron $v$ according to \cite{VarshneyChklovskii09}.  Then, let $\mc{S}$ be the set of edges deemed responsible for odor-evoked behavior according to \cite{ChalasaniBargmann07}.  If odor-evoked behavior is supervenient on this signal subgraph $\mc{S}$, then the distribution of edges in $\mc{S}$ must differ between the two classes of odor evoked behavior \cite{VP11_sigsub}.  Let $E_{uv|j}$ denote the expected number of edges from vertex $v$ to vertex $u$ in class $j$.   For class $m_0$, let $E_{uv|0}=A_{uv}+\eta$,  where $\eta=0.05$ is a small noise parameter  (it is believed that the C.~elegans connectome is similar across organisms \cite{Durbin87}). For class $m_1$, let $E_{uv|1}=A_{uv}+z_{uv}$, where the signal parameter $z_{uv}=\eta$ for all edges not in $\mc{S}$, and $z_{uv}$ is uniformly sampled from $[-5,5]$ for all edges within $\mc{S}$. For both classes, let each edge be Poisson distributed, $F_{A_{uv}|M=m_j}$= Poisson$(E_{uv|j})$.
% Let the mental property correspond to the C.~elegans exhibiting (or not exhibiting) a particular behavior (e.g., response to an odor).  Thus, one can specify $F_{M=m_1}$ and $F_{M=m_0}$, the probability of a C.~elegans exhibiting or not a particular behavior.   The class-conditional distributions $F_{B|M=m_j}$ are therefore the distributions of brain-graphs conditional on whether the C.~elegans exhibits said property.

@@

\clearpage
\bibliography{/Users/jovo/Research/latex/library}
\bibliographystyle{nature}

@@

The authors would like to acknowledge helpful discussions with J.~Lande, B.~Vogelstein, S.~Seung, and K.~Kording.

@@

>>>>

\noindent Questions and assumptions about mind-brain supervenience go back at least as far as Plato's dialogues in circa 400 BCE \cite{Plato97}.  While there are many different notions of supervenience, we find Davidson's canonical description particularly illustrative \cite{Davidson70}:
%  The mind-brain supervenience notion was canonized in 1970 with the following quote from Donald Davidson \cite{Davidson70}:
\begin{quotation}
\noindent [mind-brain] supervenience might be taken to mean that there cannot be two events alike in all physical respects but differing in some mental respect, or that an object cannot alter in some mental respect without altering in some physical respect.
\end{quotation}
Colloquially, supervenience means ``there cannot be a mind-difference without a physical-difference.''
This philosophical conjecture has potentially widespread implications.  
% We consider a special case of supervenience of considerable interest.  Specifically, this work addresses a version of a local supervenience between mental properties and brain properties, with particular emphasize on brain-graphs (i.e., connectivity structure).  Supervenience questions or assumptions are fundamental to 
% The determination of supervenience (or lack thereof) of minds on brains has potentially important implications in 
% a number of fields of inquiry.  
For example, neural network theory and artificial intelligence often implicitly assume 
a local version mind-brain supervenience \cite{Haykin2008,Ripley2008}. Cognitive neuroscience similarly seems to operate under such assumptions
% , which if falsified, might result in novel perspectives and theories 
\cite{Gazzaniga2008}.  Philosophers continue to debate and refine notions of supervenience 
% And the question of mind-brain supervenience continues to be debated amongst philosophers 
\cite{Kim2007}.  
% Moreover, many cognitive neuroscience investigations could be cast as questions
Yet, to date, relatively scant attention has been paid to what might be empirically learned about supervenience.

@@

Let $A_{uv}$ be the number of chemical synapses between neuron $u$ and neuron $v$ according to \cite{Varshney2011}.  Then, let $\mc{S}$ be the set of edges deemed responsible for odor-evoked behavior according to \cite{ChalasaniBargmann07}.  If odor-evoked behavior is supervenient on this signal subgraph $\mc{S}$, then the distribution of edges in $\mc{S}$ must differ between the two classes of odor evoked behavior \cite{VP11_sigsub}.  Let $E_{uv|j}$ denote the expected number of edges from vertex $v$ to vertex $u$ in class $j$.   For class $m_0$, let $E_{uv|0}=A_{uv}+\eta$,  where $\eta=0.05$ is a small noise parameter  (it is believed that the C.~elegans connectome is similar across organisms \cite{Durbin87}). For class $m_1$, let $E_{uv|1}=A_{uv}+z_{uv}$, where the signal parameter $z_{uv}=\eta$ for all edges not in $\mc{S}$, and $z_{uv}$ is uniformly sampled from $[-5,5]$ for all edges within $\mc{S}$. For both classes, let each edge be Poisson distributed, $F_{A_{uv}|M=m_j}$= Poisson$(E_{uv|j})$.
% Let the mental property correspond to the C.~elegans exhibiting (or not exhibiting) a particular behavior (e.g., response to an odor).  Thus, one can specify $F_{M=m_1}$ and $F_{M=m_0}$, the probability of a C.~elegans exhibiting or not a particular behavior.   The class-conditional distributions $F_{B|M=m_j}$ are therefore the distributions of brain-graphs conditional on whether the C.~elegans exhibits said property.

@@

\clearpage
\bibliography{/Users/jovo/Research/latex/library}
\bibliographystyle{naturemag}

@@

This work was partially supported by the Research Program in Applied Neuroscience. The authors would like to acknowledge helpful discussions with J.~Lande, B.~Vogelstein, S.~Seung, and K.~Kording.

@@

\newpage
\section*{Figure Legends} % (fold)
\label{sec:section_name}

% section section_name (end)
\paragraph{Figure 1} % (fold)
\label{par:figure_1}

% paragraph figure_1 (end)

C.~elegans graph classification simulation results.  The estimated hold-out misclassification rate $\hL^{n'}_{F}(g_{n})$  (with $n'=1000$ testing samples) %$\hL^{1000}_{\PP}(g_{\mt{n}})$ 
is plotted as a function of class-conditional training sample size $n_j=n/2$, suggesting that for $\varepsilon=0.1$ we can determine that $\MeB$ holds with $99\%$ confidence with just a few hundred training samples generated from $F_{MB}$. Each dot depicts $\hL^{n'}_{F}(g_n)$ for some $n$; standard errors are $(\hL^{n'}_{F}(g_{n}) (1-\hL^{n'}_{F}(g_{n}))/n')^{1/2}$.  For example, at $n_j = 180$ we have $k_n = \lfloor\sqrt{8 n}\rfloor=53$ (where $\lfloor\cdot\rfloor$ indicates the floor operator), $\hL^{n'}_{F}(g_{n}) = 0.057$, and standard error less than $0.01$. We reject $H_0^{0.1}: L^* \geq 0.1$ at $\alpha=0.01$. Note that $L^* \approx 0$ for this simulation.
